The watershed transform in ITK - discussion and new developments

### 2006-05-22 article/Article.tex
update timing results
darcs-hash:20060522205312-2fc9d-9263eb42cd5c6d0c303bd1eb2585628aa7ab2219.gz

The relative performance of the new filters are shown in
Table~\ref{tbl:perf}. The timings were obtained using the {\tt
./perf3D images/ESCells.img}. The times for steps involved in a
morphological watershed are shown in the first few columns, with the
time from a combined filter and the itk watershed shown last. It
should be noted that the itk watershed does not allow connectivity to
be modified by the user - it always uses face connected mode and
doesn't have an inbuilt mechanism for boundary selection. The existing
ITK watershed is therefore somewhat slower than the new implementation
when used to compute a traditional watershed. The new implementations
are not easily threadable and therefore may prove to be slower on some
systems. Moreover, this results doesn't show the performance in the
case where the user modify the \verb$Level$ parameters of the ITK
filter, case where the time needed to update the filter should be a lot
shorter. However, as discussed in earlier sections, the new
implementation produces more stable results than the rainfall model
and is more dedicated to a marker based approach.

\begin{table}[htbp]
\centering
\begin{tabular}{cc|ccc|cc}
\hline
FC & MB & Find min &  Label min & Ws from markers & Morph ws &  ITK ws \\
\hline
\hline
0 &      0 &      1.61 &   0.0476 & 3.72 &   6.14 &   - \\
0 &      1 &      1.59 &   0.0428 & 6.25 &   8.95 &   - \\
1 &      0 &      3.15 &   0.0465 & 7.77 &   11.5 &   6.48 \\
1 &      1 &      3.19  &  0.0462  &14.8 &   19.2  &  - \\
% 0  &    0  &     1.948  & 0.522  & 5.752  & 8.222   & 8.218  & 12.596 \\
% 0  &    1  &     1.922  & 0.516  & 6.724  & 9.162   & 9.28   & 12.61 \\
% 1  &    0  &     4.26   & 0.154  & 13.274 & 17.688  & 18.158 & 12.61 \\
% 1  &    1  &     4.284  & 0.15   & 17.23  & 21.664  & 21.76  & 12.606 \\
\hline
\end{tabular}
\caption{Execution times. Note the FC and MWL refer to FullyConnected and MarkWatershedLine.\label{tbl:perf}}
\end{table}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{cc|cccc|cc}
\hline
FC & MWL & Impose min &  ITK ws & Match labels & Change labels & Morph ws & ITK ws \\
\hline
\hline
0 &      0 &      -    &   -   &    -      & -     &  3.67 &   - \\
0 &      1 &      -    &   -   &    -      & -     &  6.53 &   - \\
1 &      0 &      5.46 &   7.8 &    0.0192 & 0.227 &  14.6 &   13.5 \\
1 &      1 &      -    &   -   &    -      & -     &  34.8 &   - \\
% 0   &  0  &  2.47776 & 8.12256 & 4.29153e-07 & 0.0990558 &  10.6994 & 3.70646\\
% 0   &  1  &  2.24303 & 8.20924 & 9.53674e-07 & 0.0977524 &  10.55   & 6.22279\\
% 1   &  0  &  5.92089 & 12.2889 & 4.29153e-07 & 0.0971172 &  18.3069 & 10.7172\\
% 1   &  1  &  6.08657 & 12.222  & 5.72205e-07 & 0.0927572 &  18.4014 & 18.4605\\
\hline
\end{tabular}
\caption{Execution times with marker based approach. Note the FC and MWL refer to FullyConnected and MarkWatershedLine.\label{tbl:perf-marker}}
\end{table}

>>>>

The relative performance of the new filters are shown in
Table~\ref{tbl:perf}. The timings were obtained using the {\tt
./perf3D images/ESCells.img} on an Athlon 64 
Processor 2800+ (1802 MHz) with 512Kb cache, 512 Mb of RAM running
Mandriva linux 64 bits with gcc 4.1.1. The input image have a size of
$371 \times 371 \times 34$.

\begin{table}[htbp]
\centering
\begin{tabular}{cc|ccc|cc}
\hline
FC & MWL & Find min &  Label min & Ws from markers & Morph ws &  ITK ws \\
\hline
\hline
0 &      0 &      1.39 &   0.0566 & 2.74 &   4.61 &   7.47 \\
0 &      1 &      1.38 &   0.056  & 4.34 &   6.53 &   - \\
1 &      0 &      2.85 &   0.0568 & 5.8  &   9.54 &   - \\
1 &      1 &      2.85 &   0.0568 & 10.5 &   14.4 &   - \\
% 0  &    0  &     1.948  & 0.522  & 5.752  & 8.222   & 8.218  & 12.596 \\
% 0  &    1  &     1.922  & 0.516  & 6.724  & 9.162   & 9.28   & 12.61 \\
% 1  &    0  &     4.26   & 0.154  & 13.274 & 17.688  & 18.158 & 12.61 \\
% 1  &    1  &     4.284  & 0.15   & 17.23  & 21.664  & 21.76  & 12.606 \\
\hline
\end{tabular}
\caption{Execution times. Note the FC and MWL refer to FullyConnected and MarkWatershedLine.\label{tbl:perf}}
\end{table}

The times for steps involved in a
morphological watershed are shown in the first few columns, with the
time from a combined filter and the itk watershed shown last. It
should be noted that the itk watershed does not allow connectivity to
be modified by the user - it always uses face connected mode and
doesn't have an inbuilt mechanism for boundary selection. The existing
ITK watershed is therefore somewhat slower than the new implementation
when used to compute a traditional watershed. The new implementations
are not easily threadable and therefore may prove to be slower on some
systems. Moreover, this results doesn't show the performance in the
case where the user modify the \verb$Level$ parameters of the ITK
filter, case where the time needed to update the filter should be a lot
shorter. However, as discussed in earlier sections, the new
implementation produces more stable results than the rainfall model
and is more dedicated to a marker based approach.

@@

\begin{table}[htbp]
\centering
\begin{tabular}{cc|cccc|cc}
\hline
FC & MWL & Impose min &  ITK ws & Match labels & Change labels & Morph ws & ITK ws \\
\hline
\hline
0 &      0 &      2.32 &   6.81 &   0.0295 & 0.273 &  3.12 &   9.43 \\
0 &      1 &      -    &   -    &   -      & -     &  5    &   - \\
1 &      0 &      -    &   -    &   -      & -     &  6.57 &   - \\
1 &      1 &      -    &   -    &   -      & -     &  11.6 &   - \\
% 0   &  0  &  2.47776 & 8.12256 & 4.29153e-07 & 0.0990558 &  10.6994 & 3.70646\\
% 0   &  1  &  2.24303 & 8.20924 & 9.53674e-07 & 0.0977524 &  10.55   & 6.22279\\
% 1   &  0  &  5.92089 & 12.2889 & 4.29153e-07 & 0.0971172 &  18.3069 & 10.7172\\
% 1   &  1  &  6.08657 & 12.222  & 5.72205e-07 & 0.0927572 &  18.4014 & 18.4605\\
\hline
\end{tabular}
\caption{Execution times with marker based approach. Note the FC and MWL refer to FullyConnected and MarkWatershedLine.\label{tbl:perf-marker}}
\end{table}
